\documentclass[twocolumn]{article}
\usepackage{epsfig}
\usepackage{psfig}
\usepackage{graphicx}
\usepackage{url}
\usepackage{times}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green]{hyperref}
\setlength{\columnsep}{20pt}
\newcommand{\SA}{Simulated Annealing~}
\makeatletter
\def\verbatim{\small\@verbatim \frenchspacing\@vobeyspaces \@xverbatim}
\makeatother
\begin{document}

\title{{\bf The Application of Simulated Annealing in Polynomial Solver}\\ }

\author{Xin Wang\\ \vspace{0.5cm}\\
 10302010023\\ \vspace{0.01cm}\\
 xin\_wang@fudan.edu.cn\\}

\date{}
\maketitle
\begin{abstract}
\SA is a widely-adopted physical computing algorithm, which is a suitable candidate to estimate the extreme points of a cost function. This paper implements a tiny \SA polynomial solver and proposes two versions implemented in floating point number and fixed point number respectively. Moreover, this paper analyzes the architectural characteristics of \SA solver in order to draw some insights about the program behavior of \SA solver. Furthermore, this paper measures the execution statistics of both two versions as well as the error rate of the fixed point one so as to explore the potential of performance increase.
\end{abstract}

\input{introduction}

\input{related}

\input{design}

\input{analysis}

\input{discussion}

\input{conclusion}


\section{Acknowledgements}
Thanks are due to our lecturer Mr. David Fagan who gave us a vivid and thought-provoking representation of natural computation topic and my tutor Prof. Zhang and my upperclassman Mr. Dai who gave me much precious help in primitive scientific research skills.

\bibliographystyle{abbrv}
\bibliography{biblio}

\end{document}

